%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% 
%% Saminda Abeyruwan's resume
%%   - based off work by Michael DeCorte 
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%



%%
%% The following code sets up the document formatting
%%

%this assumes that res_yy.sty is in some path
\documentstyle[hyperref, margin, line]{res_yy}

\hypersetup{backref,pdfpagemode=Full,colorlinks=true,backref}

\addtolength{\oddsidemargin}{-0.50in}
\addtolength{\voffset}{-0.30in}
\addtolength{\textwidth}{1.45in} \addtolength{\textheight}{2.00in}

\renewcommand{\namefont}{\LARGE\textbf}



%%
%% The following code defines some macros for terms which have raised font
%% (ie 4\fourth would result 4th with the 'th' raised (superscripted)
%%


%%
%% starting the actual document
%%

\begin{document}

%the name in big fonts at the top of resume
%this is left aligned
\name{Saminda Abeyruwan}

%this is right aligned
\address{\bf{(305) 457 9753} $\circ$
\bf{\href{http://linkedin.saminda.org}{http://saminda.org}} $\circ$ 
\bf{samindaa@gmail.com} }

\begin{resume}


%%
%% This section of code is inelegant, but I'm too lazy to fix it
%%

%\section{\textsc{Interest}}
%To obtain a software development internship that provide an opportunity for
%advance within the enterprise.
\vspace{-5mm}
\section{\textsc{Education}}

\textbf{University of Miami, Coral Gables, FL} \hfill Fall 2010 -- July 15$^{\mbox{th}}$, 2015 \\
Ph.D. in Computer Science (Expected) \hfill GPA: 3.98 \\
\newline
\textbf{University of Miami, Coral Gables, FL} \hfill Fall 2008 -- Spring 2010 \\
M.S. in Computer Science \hfill GPA: 4.0 \\
\newline
\textbf{University of Moratuwa, Sri Lanka} \hfill November 2000 -- November 2004 \\ 
B.Sc. (Honors) in Electrical Engineering \hfill GPA: 3.79 -- Ranked 1$^{\mbox{st}}$ out of 60



%%
%% the meat of the resume starts now
%%

\begin{formatb}
  \title{l}\dates{r}\\
  \body\\
\end{formatb}

\vspace{-2mm}
\section{\textsc{Employment}}

\title{\textbf{Research Assistant: University of Miami, Coral Gables, FL}}
\dates{Fall 2010 - Present}
%\begin{position}
%$\circ$  Taught Semantic Web and Technologies graduate course during Fall 2011.  
%\end{position}


%\title{\textbf{Software Developer:  Center for Computational Science, Miami}}
%\dates{Summers 2011 -- 2014}
\begin{position}
\textit{As a software engineer/developer I have completed several projects including:}\newline
\textbf{Bio Assay ontology} (\url{http://bioassayontology.org/}): \newline
$\circ$ Designed software tools to mitigate the knowledge acquisition bottleneck and 
implemented them in C\texttt{++} and Java. \newline
$\circ$ Design parallel algorithms for near-real-time reasoning on OWL 2 ontologies with large 
assertional boxes and implemented thm using MapReduce programming model. \newline
\textbf{RegenBase Ontology} (\url{http://regenbase.org/}) : \newline 
$\circ$ Used text mining methods to extract knowledge from about 1,500 technical paper to develop 
ontologies to link data 
and results from studies on nervous system injuries and diseases and implemented 
them using C\texttt{++} and 
OpenNLP. \newline $\circ$ Developed  various Prot\'{e}g\'{e} plugins to 
expedite knowledge acquisition, and assay annotations (Java).


\end{position}

\title{\textbf{Teaching Assistant: University of Miami, Coral Gables, FL}}
\dates{Fall 2008 - Spring 2010}
\begin{position}
$\circ$  Taught and graded computer science courses during the Fall and Spring
semesters of the 2008 -- 2010 academic years. \newline $\circ$   Received the best TA award in 
recognition of the teaching
performance.
\end{position}

\title{\textbf{Senior Software Engineer/Technical Lead: WSO2 Inc, Sri Lanka}}
\dates{August 2005 -- August 2008}
\begin{position}
$\circ$ Developed middleware applications using the principles of service-oriented 
architecture and Apache Web services projects (Java).   \newline $\circ$ 
Managed a software team to integrate the Web Services Application Server with Apache Web services. 
Developed enterprise service bus with Apache Synapse project.\newline $\circ$ Researched and 
developed 
applications that utilized OSGi technologies. 
\end{position}

%\vspace{-2mm}
%\section{\textsc{Additional Experience and Awards}}

\begin{formatb}
  \employer{l}\dates{r}\\
  \body\\
\end{formatb}

%\employer{\textbf{Research Assistant: University of Miami, Coral Gables, FL}}
%\dates{Fall 2010 - Present}
%\begin{position}
%$\circ$  Taught Semantic Web and Technologies graduate course during Fall 2011.  
%\end{position}


%%
%% We use the same formatting for projects as for work experience
%% Shown below is the formatting used previously
%%
%%  \begin{formatb}
%%    \employer{l}\title{r}\\
%%    \location{l}\dates{r}\\
%%    \body\\
%%  \end{formatb}
%%
%% 
%%  Note that \location is now being used for non-location information
%%


\begin{formatb}
  \employer{l}\dates{r}\\
  \body\\
\end{formatb}

\vspace{-2mm}
\section{\textsc{Technical Experience and Projects}}

\employer{\textbf{Embedded Systems}}
\dates{Spring 2013 -- Present}
\begin{position}
$\circ$ Developed  unification methodologies to detect abnormal events using embedded devices 
(C\texttt{++}). \newline
$\circ$ Developed supervised  and reinforcement learning algorithms for prediction and control 
problems.
\end{position}

\employer{\textbf{RoboCup Soccer}}
\dates{Fall 2010 - Present}
\begin{position}
$\circ$ Used the RoboCup Standard Platform (NAO humanoid robots) and the 3D Soccer Simulation 
League as 
test environments to research on real-time reasoning to build autonomous agents (C\texttt{++}). 
\newline $\circ$  
Used 
general value function in reinforcement learning as a method to  represent predictive knowledge in 
role assignments in soccer formations (C\texttt{++}).
\end{position}

\employer{\textbf{Member: Apache Software Foundation}}
\dates{August 2005 - Present}
\begin{position}
$\circ$  Apache Web Services project committer  and project management committee (PMC)  member.
\end{position}





%%
%% This section could also use more formatting, but looks ok, as is
%%

%\section{\textsc{Qualifications}}

%\emph{Programming Languages}: \Cplusplus, \CSharp, Cg, HLSL, ARB assembly, SML, OCaML, PHP, MySQL, Java, Python, Perl, MIPS assembly

%\emph{Libraries and Tools}: Vim, STL, DirectX, OpenGL, \LaTeX, GIMP, Adobe Suite, Macromedia Suite, MatLab, Mathematica, Microsoft Visual Studio, GCC, GDB


%%
%% Note that we're redefining the formatting
%% We only have one row of information now, instead of two
%%


\vspace{-2mm}
\section{\textsc{Languages and Technologies}}

\employer{\textbf{C/C\texttt{++}, Java, and Matlab}}
\dates{~}
\begin{position}
$\circ$ CUDA, Hadoop, WebGL, Energia, Ubuntu, Windows, Eclipse IDE, Make, Maven, and
Git.
\end{position}

\vspace{-2mm}
\section{\textsc{Professional}}
\employer{\textbf{Memberships}}
\dates{~}
\begin{position}
$\circ$ Student members of ACM, IEEE, and IAAA.
\end{position}


\employer{\textbf{Awards}}
\dates{~}
\begin{position}
$\circ$ Best teaching assistant (2010); RoboCup $\sim$ 1$^{\mbox{st}}$ in Europe Open 2011;  
2$^{\mbox{nd}}$ in World Cup, and 2$^{\mbox{nd}}$ Asian Open 2012; 2$^{\mbox{nd}}$ in World Cup, 
2$^{\mbox{nd}}$ in U.S. Open, and  3$^{\mbox{rd}}$ in Asian Open 2014; 1$^{\mbox{st}}$ in U.S. Open 
2015. 
\end{position}


%%
%% Nothing special here, just a normal table
%%

%\section{\textsc{Course Work}}
%  \begin{tabular}{lllll}
%  Information Networks   & \ \ & Machine Learning    & \ \ & Theory of Computation \\ 
%  Computer Graphics      & \ \ & Machine Vision      & \ \ & Programming Languages \\
%  Software Engineering   & \ \ & Algorithms          & \ \ & Artificial Intelligence     \\
%  Operating Systems      & \ \ & Databases           & \ \ & Computer Architecture \\
%  Numerical Methods      & \ \ & Graph Theory        & \ \ & Differential Equations      \\
%  Probability Theory     & \ \ & Number Theory       & \ \ & Differential Geometry       \\
%  Advanced Calculus      & \ \ & Abstract Algebra    & \ \ & Advanced Combinatorics   \\
%  \end{tabular}


\end{resume}
\end{document}
